Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2016-01-22 paper.tex
Text wrapping
Text wrapping and whitespace
Minor wording in first paragraph of conclusion

\begin{figure}[H]
\centering
\includegraphics[width=0.65\textwidth]{figures/wake_trans_totals}
\caption{Normalized transport totals from Figures~\ref{fig:mom-bar-graph} and
\ref{fig:K-bar-graph} plotted \textit{versus} the Reynolds number.}
\label{fig:wake-trans-totals}
\end{figure}
%\unskip

@@

In this study, it was demonstrated that the performance of a high solidity
($c/R=0.28$) cross-flow turbine becomes essentially $Re$-independent at a
Reynolds number based on a turbine diameter of $Re_D \approx 10^6$ or an
approximate Reynolds number based on a blade chord of $Re_c \approx 2 \times
10^5$. The power coefficient values on the left-hand side of the
$C_P$-$\lambda$ curve are reduced more than those on the right-hand side at low
$Re$ due to deeper stalling. The $Re$-independent threshold corresponds to that
at which the foil suction surface boundary layer becomes turbulent before having
to recover static pressure against the adverse pressure gradient, highlighted in
\cite{Lissaman1983, McMasters1980, Carmichael1981}.

>>>>

    \includegraphics[width=0.65\textwidth]{figures/wake_trans_totals}

    \caption{Normalized transport totals from Figures~\ref{fig:mom-bar-graph}
        and \ref{fig:K-bar-graph} plotted \textit{versus} the Reynolds number.}

    \label{fig:wake-trans-totals}
\end{figure}
%\unskip

@@

In this study, it was demonstrated that the performance of a high solidity
($c/R=0.28$) cross-flow turbine becomes essentially $Re$-independent at a
Reynolds number based on the turbine diameter $Re_D \approx 10^6$ or an
approximate Reynolds number based on the blade chord $Re_c \approx 2 \times
10^5$. The power coefficient values on the left-hand side of the $C_P$-$\lambda$
curve are reduced more than those on the right-hand side at low $Re$ due to
deeper stalling. The $Re$-independent threshold corresponds to that at which the
foil suction surface boundary layer becomes turbulent before having to recover
static pressure against the adverse pressure gradient, highlighted in
\cite{Lissaman1983, McMasters1980, Carmichael1981}.
